\section*{1. Introduction}
\addcontentsline{toc}{section}{1. Introduction}

\subsection*{Product Vision}
\addcontentsline{toc}{subsection}{Product Vision}
The target audience of our app are SETU students who have access to Moodle specifically, who are looking for a space where all their resources and different applications are easily accesible.
\hfill \break

The SETUP app (also known as South East Techonological University Personalised) is an application that acts as a hotspot between multiple SETU services, allowing you to access anything from exam papers to lecture contacts to Outlook to Moodle, all within the one space that include important features such as discussion groups, calendars, class timetables, and a map feature. 
\hfill \break

Unlike Moodle, which already has access to a lot of these, it is formatted in a way that makes it easier to navigate and makes all essential services centralised while also letting departments and services, such as the Computer and Maths Learning Centre, to get in touch with students directly and notify them of events and such.
\hfill \break

In our own experience, having resources split across multiple platforms is extremely hard to work with, but with SETUP, both lecturers and students can stay in frequent contact and on top of work and schedules.
\hfill \break

Our Product, SETUP, gives SETU students a completely integrated, secure and student-focused experience that brings campus services, academic information and updates that happen in real time into one place.

\subsection*{Similar App A - XTiles}
\addcontentsline{toc}{subsection}{Similar App A - XTiles}
XTiles is a workspace and visual productivity platform that is aimed towards daily planning, personal tasks, note-taking and project management. 
It is more of a visual board rather than a document and because of this it is focused toward students and creative professionals who prefer to 
see things visually organised. XTiles feature of drag-and-drop like moving texts, links and images makes it easy to arrange around
your workspace. It is user friendly and suitable for customers to create schedules and their weekly study plans. 

\hfill \break
Good things about xTiles:
\begin{itemize}
\item Flexible visual workspace where you can customize to your own needs. (Enables the user to add texts, images, links, etc.)
\item It supports real-time multi-user collaboration (Teams can work on a board together).
\item Great to make plans, brainstorms and organizing.
\item It is cross-platform, so you can access it through multiple devices.
\item It’s integrated with other applications like Google Calendar. Allows to sync with events or deadlines.
\item  With the templates they provide, they are visually pleasing and excellent for those with ADHD.
\item Special offers for students.
\end{itemize}
\hfill \break
Bad things about xTiles:
\begin{itemize}
\item  There isn’t a lot of offline activities to do, it is rather more internet accessible.
\item It can be overwhelming at first because there is numerous of tools to go through and learn.
\item The free plan is fairly limited and must pay for unlimited workspaces. 
\end{itemize}

\subsection*{Similar App B - Studo}
\addcontentsline{toc}{subsection}{Similar App B [PLACEHOLDER]}

The main thing Studo offers is an app which combines both academic and campus services into one place.
For example, SETU Timetables for students and Moodle are two seperate platforms, but Studo combines these together and lets you access them from the same application.
They have partnerships and supply software to over 60 different universities across Germany and Austria.
Their mobile app has over 500,000 downloads, not including desktop downloads.

\hfill \break
Good things about Studo:
\begin{itemize}
  \item Combines lots of daily university/on-campus services (email, calendar, grades, timetables)
  \item Real-Time polls and push alerts
  \item Easy to integrate existing records and student information
  \item Easily acessable course and grade overview with key dates for assignments and uploads
  \item Both synced and accesible from multiple devices
  \item University news feed and up-to-date food menus
\end{itemize}

Bad things about Studo:
\begin{itemize}
  \item The overall application is extremely basic. Many of the features are extremely limited in what they can do.
  \item Many tools and featurs are admin controlled, not easy for students to customise what they see, etc
  \item Not accesible for students, looking at reviews it looks like students struggle connecting their student accounts to the application
  \item The calander is limited on what you can add/info you add to it
  \item Chat feature between students is heavily moderated and deletes things that don't go against the platforms rules
  \item 2FA and login features are unreliably and often don't work, affecting time pressured situations
\end{itemize}

\subsection*{Features}
\addcontentsline{toc}{subsection}{Features}
etc. etc.