\section*{2. Personas}
\addcontentsline{toc}{section}{2. Personas}

\subsection*{Definition}
\addcontentsline{toc}{subsection}{Definition}
A user persona imagines a specific type of user for a given platform. e.g. SETUP, a student services app, may consider students, lecturers, and/or guests. Product expectations may vary depending on user background, education and skillset.\\ 

By conceptualising the types of users this product seeks to attract; personas assess what features are best to proritise. It also suggests what features may require further development, or scrapping entirely, in order for the product to be suitable for its demographics.
 
\subsection*{1. Connor Byrne, a Department of Science lecturer}
\addcontentsline{toc}{subsection}{Persona 2}
Byrne is a 42 year old lecturer in the Department of Science at SETU. He specifically lecturers in classes relating to Biology or Pharmaceuticals. With over 10 years of experience in teaching in this field, he delivers modules to undergraduates, supervises final year research projects, and contributes to the research conducted by the university. \\

Byrne manages large amounts of students across different groups each semester, often trying to balance lecturing, grading, meetings, research deadlines, and to stay in touch with students who may have questions. Byrne finds students contacting him across a plethera of platforms, most being Slack, Moodle, Outlook, Teams, etc. He finds that switching between these apps to keep track of messages is time-consuming and inefficient. \\

Byrne would benefit from an app like SETUP, which allows for all these platforms to be confined to a central hub. This would also help him manage schedueling meetings with students and staff, grading, exam timetables, as these can be tasks that are done automatically. Reducing the amount of repetitive tasks and simplifying it down to a reporting process would significantly improve his workflow. \\

Seemless integration and local navigation of all the socail platforms that the university uses will allow him to stay up-to-date and in frequent contact with his research group, fellow staff, and all the students that attempt to reach out to him. \\ 

\subsection*{2. Maria Angelo, a mature nursing student}
\addcontentsline{toc}{subsection}{Persona 3}
Maria Angelo, 46 years old, mother of two daughters. She is a nurse who works in a local hospital, aiding patients in need of care. She graduated out of nursing school when she was 22 years old in the Philippines. By age 30 she had the opportunity to work in Ireland, where she met her lovely husband 2 years later. They live in the suburb with their daughters, a 12 years old and and a 14 year old who attend first and third year of secondary school respectively. \\ 

Maria has been in the nursing field for 23 years, now she wants to specialise in a different area which requires certification. She decides to go back to college and start studying again. Maria is a busy woman, now that she must balance returning to education, working overtime in hospital and minding her daughters. With her busy schedule, she would miss deadlines for her assignments and would have to contact her lecturers to have an extension. \\ 

With the help of SETUP, she can create her schedules, check lists of her tasks and additional information. This will assist her time schedule, as it includes an automated timetable specifically for the user. There's a board for the user to write up their personal to-do list and it traces deadlines that is set by Moodle. She can email her lecturers through the app as well as receiving them. \\

Instead of going through different applications for peculiar tasks, SETUP would allow her do it all in one application. The built-in integrations and neat GUI will help set personal schedules, tick off her to-do lists and request deadline extensions when necessary to her lecturers.

\subsection*{3. Jane, an accounting student with accessibility concerns}
\addcontentsline{toc}{subsection}{Persona 4}

Jane is a 20 year old first year undergraduate, pursuing a BA (Hons) in Accounting at SETU. She has been receiving good grades and is an active member of the SETU snowboarding society. She commutes two hours by bus from Wexford for her 9am-5pm weekly classes. \\

She has experienced difficulty in navigating the various grants and accomodation forms, and would appreciate an app that makes booking appointments with services such as MABS, counselling or the disability office more straightforward. \\

ADHD can cause Jane to become disorganised with her appointments, because of this she keeps a physical journal. Unfortunately, she does not always remember to keep this journal updated, so having an automated digital calendar  for academic and social events  would be useful. \\

Jane also uses a low vision setting on her phone for app navigation, she's noticed a lack of support in many online services for this feature. SETUP should consider the accessibility needs of users like Jane when developing upon its services.\\






