\section*{3. Scenarios}
\addcontentsline{toc}{section}{3. Scenarios}

\subsection*{Definition}
\addcontentsline{toc}{subsection}{Definition}
A user scenario describes how user demographics interact with our SETUP application. No one scenario is an all-encompassing demonstration of a product's features, rather an example of a specific usecase.
\subsection*{Scenario 1 - MCQs}
\addcontentsline{toc}{subsection}{Scenario 1}
One module that Byrne teaches is structured to have many small bi-weekly Mulitple Choice Question quizzes based on material and topics covered over the weeks. Byrne is preparing teaching materials for this module at the beginning of the semester but has previously found it difficult to be consistent with reminders about the quizzes as announcements across Moodle, email, and in-class reminders were often missed or overlooked.\\

Using SETUP, Byrne can schedule all the quizzes through the built in academic calender, which will automatically sync with students personal timetables. He can choose for these quizzes to send push notification alerts to the students if it is a certain amount of time before each quiz, for example, 2 days and 24 hours before.\\

Byrne can also contact students easier through SETUP and stay consistently in touch with any questions or queries about the MCQ without needing to check multiple platforms. Students can view the quiz details, deadline, study material, and any feedback after the quiz. \\

This helps Byrne improve student engagement and fewer missed assesments, but also allows him to spend less time sending repeated reminders or responding to questions across multiple platforms which allows him more focus on teaching and research.\\


\subsection*{Scenario 2 - Time Management}
\addcontentsline{toc}{subsection}{Scenario 2}
Mario Angelo is a 46 year old mother of two daughters. She works as a nurse and is also a mature student in SETU. She's always busy every weekday dropping her daughters to and from school, going to her classes midday and then working in the evenings. She loves being occupied but she lacks time management.\\

Sometimes, it's difficult for her to keep on track when she needs to submit her assignments and would miss the deadlines. Since Maria and her husband alternate times to pick up their daughters, Maria would forget and her husband would remind her, leaving her daughters waiting more outside of school hours or either making them late to school by a minute. This also affects Maria by being late to her own class in the mornings.\\

With the help of SETUP, she can benefit from the app by scheduling her day. The To-Do and Notes Tool icon, she can track her deadlines, and jot down notes to write before her day starts. The app lets you add a template to add schedules and times. This is easy for Maria, so she knows what time of the day to get things done.\\

If she misses a deadline, SETUP has an email integration where it allows the user to connect to several email accounts to one inbox. It enables her to receive notifications from that application. It supports her so she doesn't have to go from app to app.\\

This improves Maria's organising skills. Now she doesn't need to remind herself but with the support of the application, it lets her keep on track. She is able to send emails to lecturers just incase she needs to have extensions and also receive the email all in one application. 

\subsection*{Scenario 3 - Accomodations \& Services}
\addcontentsline{toc}{subsection}{Scenario 3}
Jane is a first year accounting student at SETU, and she needs to make an appointment with the counsellor on campus along with submitting her disability accommodation form. Previously Jane has faced some difficulty with doing these things as the booking system and the forms are across different platforms and the process isn't straight forward.\\

With SETUP, Jane has access to the counselling services and disability office on the app services section. The app gives her appointment availability in real time where she can book a slot that suits her schedule. When the booking is made, it automatically gets added to her SETUP calendar with reminder push notifications as the appointment gets close. which is helpful to her because of the organisational challenges that can be caused by her ADHD.\\

Jane can also find and complete her disability accommodation form through the SETUP app instead of having to search through different tabs on the SETU website. The form can be accessed in the app which is also compatible with her low vision phone settings, making the process easy to navigate.\\

The straightforward layout of SETUP  allows Jane to independently manage her college responsibilities without the stress of finding services across multiple platforms. It also ensures that she is less likely to miss appointments or deadlines, which allows her to focus more on her studies and college life.

\subsection*{Scenario 4 - Campus Orientation}
\addcontentsline{toc}{subsection}{Scenario 4}
Anthony has decided to attend the first prospective student orientation at SETU Waterford. Using the SETUP app he was able to view a map of the Cork Road campus, labelled with current events, informational stands, bathrooms, etc. in advance of his visit. \\

As a guest user, he is able to enroll in a number of trial modules for various courses covered throughout the day, with downloadable resources such as infographics, Q\&As and presentations used throughout on campus demos.\\

Pre-registration for various smaller lab demos were opened throughout the day, Anthony decided to attend a small lab demo for a robotics project he took interest in. Interactivity throughout the demo was made easier using the apps in-built question submission function.\\

The SETUP app allows Anthony to spend more of his orientation engaging in the activities he's interested in, with the assurance he won't be missing out on events or getting lost on-campus without guidance when on-campus guides are unavailable. 

\subsection*{Scenario 5 - P2P Events}
\addcontentsline{toc}{subsection}{Scenario 4}
Kiara wants to arrange a group event for her first year Computer Science Undergraduate group, however engagement with her peers is difficult to maintain. She wants to use a service more dedicated to P2P events than normal messenger apps, ideally this service is cohesive with what students are already used to. \\

By sending alerts through the SETUP app, P2P news becomes integrated into the student workflow already established. Resources relevant to events are centralised to a 'P2P' module, with online participation and records available for viewing after live events.\\

Kiara can keep tabs on her P2P group engagement individually, without needing a third-party app that blurs the line between professional and interpersonal relationship between peers. She can add events to the SETUP campus map for individual students at scheduled times, as well as receiving polls and feedback from peers in an organised format.