\section*{4. User Stories}
\addcontentsline{toc}{section}{4. User Stories}

\subsection*{Definition}
\addcontentsline{toc}{subsection}{Definition}
Describes a sequence of interactions with the SETUP system, rather than the high-level detail approach of user scenarios.

\subsection*{User Story 1 - Research Group}
\addcontentsline{toc}{subsection}{User Story 1}
\textbf{As a Lecturer who also works in research groups within the university, I want:}
\begin{itemize}
  \item To be able to quickly contact or jump between conversations with students and with the research group.
  \item To provide fast information to students about assesments, deadlines, changes to timetables, etc.
  \item To easily share resources such as lecture notes, links to resources,  file uploads, etc, with other peeople on the platform.
  \item To manage all communication in a clean and efficient manner to keep in contact and up-to-date.
\end{itemize}

\subsection*{User Story 2 - Platform Moderation}
\addcontentsline{toc}{subsection}{User Story 2}
\textbf{As a department staff member who helps moderate the platform, I want:}
\begin{itemize}
    \item To manage and update university-wide announcemnts, events, important notices, etc.
    \item To have the ability to help solve user-realted issues, such as login problems or incorrect user information.
    \item To control access permissions for different user roles, such as students, lecturers, department leads, etc.
    \item To review feedback and reports submitted by users to improve the platform.
\end{itemize}

\subsection*{User Story 3 - Campus Participation}
\addcontentsline{toc}{subsection}{User Story 3}
\textbf{As a student who wants to get more involved on campus, I want to:}
\begin{itemize}
    \item View a list of clubs and societies that are available in my college
    \item Be able to sort the list according to my interests and preferences
    \item Register for clubs and societies through the app
    \item Get updates and notifications on meetings and events in the society
    \item Communicate with other members of the clubs and societies through the app
\end{itemize}

\subsection*{User Story 4 - Time Management}
\addcontentsline{toc}{subsection}{User Story 4}
\textbf{As a student who finds it difficult to manage their time, I want to:}
\begin{itemize}
    \item Have the ability to plan my tasks and classes
    \item Get reminders regarding future deadlines and exams
    \item Be able to set goals and monitor my progress towards them
    \item Have the ability to connect with other students for study groups and support
    \item Use the app to access resources and materials for my courses easily
\end{itemize}

\subsection*{User Story 5 - Math Support Services}
\addcontentsline{toc}{subsection}{User Story 5}
\textbf{As a Computer science student struggling with their math modules, I want to:} 
\begin{itemize}
\item Book appointments at the maths learning center directly through SETUP so the process is easy and clear to navigate.
\item Find students that are in a similar struggle so that I can either join an already formed study group or create one.
\item Get notified when appointments become available, when cancelations occur e.g. exam season. Recommended outside resources around exam season when appointments are unavailable.
\item Access to relevant resources to material and topics covered in class. e.g. pdfs
\item Track progress made during maths support sessions via SETUP, identify strong/weak areas to pay attention to.
\end{itemize}

\subsection*{User Story 6 - Campus Orientation}
\addcontentsline{toc}{subsection}{User Story 6}
\textbf{As a leaving cert student attending orientation, I want to:} 
\begin{itemize}
\item Navigate the campus map for areas of interest e.g. events with clear markers
\item Be notified of scheduled events available
\item Pre-register for campus tours/lab demos
\item Download maps and relevant resources for offline use
\end{itemize}

\subsection*{User Story 7 - P2P Event Organisation}
\addcontentsline{toc}{subsection}{User Story 6}
\textbf{As a P2P Volunteer leader, I want to:} 
\begin{itemize}
\item Create and manage events and students within my course group
\item Send event alerts and add to academic calendars
\item Receive feedback e.g. polls from attendees
\item Chat with students, lecturers and other P2P volunteers on a moderated platform
\end{itemize}

\subsection*{User Story 8 - Library Services}
\addcontentsline{toc}{subsection}{User Story 6}
\textbf{As a SETU librarian, I want to:} 
\begin{itemize}
\item Access and provide e-books, scientific journals, articles etc. within the app
\item Track requested and loaned/overdue books
\item Promote workshops and other time sensitive events, e.g. extended opening hours
\item Manage private room/pod bookings
\end{itemize}

